---
title: "LBB1"
author: "Luthfi"
date: "2023-09-23"
output: html_document
---
***1. REAL ESTATE MELBOURNE***

This is a snapshot of a dataset created by Tony Pino.
link: https://www.kaggle.com/datasets/dansbecker/melbourne-housing-snapshot

It was scraped from publicly available results posted every week from Domain.com.au. He cleaned it well, and now it's up to you to make data analysis magic. The dataset includes Address, Type of Real estate, Suburb, Method of Selling, Rooms, Price, Real Estate Agent, Date of Sale and distance from C.B.D.

**Notes on Specific Variables**
Rooms: Number of rooms

Price: Price in dollars

Method: S - property sold; SP - property sold prior; PI - property passed in; PN - sold prior not disclosed; SN - sold not disclosed; NB - no bid; VB - vendor bid; W - withdrawn prior to auction; SA - sold after auction; SS - sold after auction price not disclosed. N/A - price or highest bid not available.

Type: br - bedroom(s); h - house,cottage,villa, semi,terrace; u - unit, duplex; t - townhouse; dev site - development site; o res - other residential.

SellerG: Real Estate Agent

Date: Date sold

Distance: Distance from CBD

Regionname: General Region (West, North West, North, North east …etc)

Propertycount: Number of properties that exist in the suburb.

Bedroom2 : Scraped # of Bedrooms (from different source)

Bathroom: Number of Bathrooms

Car: Number of carspots

Landsize: Land Size

BuildingArea: Building Size

CouncilArea: Governing council for the area

```{r}
#Read data csv
melb <- read.csv("data_input/melb_data.csv")

#install package dplyr to manipulate character data
library(dplyr)

```

***2. DATA PREPERATION***
```{r}
#First, we read the .csv file and use only the relevant columns
melb
```


```{r}
# Removing unnecessary columns using select()
melb2 <- melb[,!names(melb) %in% c("Address", "Postcode", "Lattitude", "Longtitude", "Propertycount", "CouncilArea", "YearBuilt")]
melb2
```

```{r}
# Converting Date datatype
#Converting Date
melb2$Date <- as.Date(melb2$Date, format = "%d/%m/%Y") 

#Converting as Factor
melb2$Suburb <- as.factor(melb2$Suburb)
melb2$Method <- as.factor(melb2$Method)
melb2$Type <- as.factor(melb2$Type)
melb2$Regionname <- as.factor(melb2$Regionname)


#Converting as Interger
melb2$Bedroom2 <- as.integer(melb2$Bedroom2)
melb2$Bathroom <- as.integer(melb2$Bathroom)
melb2$Car <- as.integer(melb2$Car)
melb2$Landsize <- as.integer(melb2$Landsize)
melb2$BuildingArea <- as.integer(melb2$BuildingArea)

```

```{r}
# Removing NA Rows and "0"
melb2 <- melb2[!is.na(melb2$BuildingArea), ] #Removing rows that has NA BuildingArea
melb2 <- melb2[melb2$Landsize != 0, ]
melb2
```
```{r}
#Checking the string and uniques
str(melb2)
unique(melb2$Regionname)
```
```{r}
#Renaming Categories for Regionname
melb2 <- melb2 %>%
  mutate(Regionname = recode(Regionname, "Northern Victoria" = "Northern Metropolitan")) #Changing north

melb2 <- melb2 %>%
  mutate(Regionname = recode(Regionname, "Eastern Victoria" = "Eastern Metropolitan")) #Changing east

melb2 <- melb2 %>%
  mutate(Regionname = recode(Regionname, "Western Victoria" = "Western Metropolitan")) #Changing west

```


***3. DATA EXPLORATION***

```{r}
# Creating Price Per Squaremeter Column
melb2$PricePerSQM <- (melb2$Price / melb2$Landsize)

#Removing outlier
Q1 <- quantile(melb2$PricePerSQM, 0.25)
Q3 <- quantile(melb2$PricePerSQM, 0.75)
IQR <- Q3 - Q1
LB <- Q1 - 1.5*IQR
UB <- Q3 + 1.5*IQR

melb2 <- subset(melb2, PricePerSQM >= LB & PricePerSQM <= UB)
```


```{r}
#Number of Rooms in Building
hist(melb2$Rooms)
mean(melb2$Rooms) # Center of Data = 2.977419 (Rooms)

#Distance
hist(melb2$Distance)
median(melb2$Distance) # Center of Data = 9.2 (Distance)

#Bedroom2
hist(melb2$Bedroom2)
median(melb2$Bedroom2) # Center of Data = 3 (Bedroom)

#Bathroom
hist(melb2$Bathroom)
median(melb2$Bathroom) # Center of Data = 1 (Bathroom)

#Car
hist(melb2$Car)
median(melb2$Car) # Center of Data = NA (Car)

#BuildingArea
hist(melb2$BuildingArea)
median(melb2$BuildingArea) # Center of Data = 126 (Building Area)
```
```{r}
#Top 10 suburb with the highest number of sold properties

freq_suburb <- table(melb2$Suburb) # Create frequency table
freq_suburb_df <- as.data.frame(freq_suburb) # Create data frame
colnames(freq_suburb_df) <- c("Suburb", "PropertiesSold") # Renaming columns
freq_suburb_df <- freq_suburb_df[order(-freq_suburb_df$PropertiesSold),]
top10_freq_suburb <- freq_suburb_df[1:10, ]
top10_freq_suburb
```



```{r}
# Top 10 Suburb with highest average of buying price per square meter
average_price <- melb2 %>%
  group_by(Suburb) %>%
  summarise(Average_Price_Per_Square_Meter = median(PricePerSQM, na.rm = TRUE)) # Creating a table
average_price <- average_price[order(-average_price$Average_Price_Per_Square_Meter),] # Sorting order
colnames(mean_price) <- c("Suburb", "Average price Per SQM") # Renaming columns
top10_freq_suburb2 <- mean_price[1:10, ]
top10_freq_suburb2

```


```{r}
boxplot(melb2$PricePerSQM~ melb2$Type,horizontal = F)
# h - house,cottage,villa, semi,terrace
# u - unit, duplex
# t - townhouse; dev site - development site
```
Dari boxplot di atas, ditemukan bahwa Tipe residen Unit memiliki median harga per meter persegi tertinggi dibandingkan dengan tipe  Town House.

```{r}
#Plotting Price PerSQM and Distance to CBD
plot(melb2$PricePerSQM~ melb2$Distance)
cor(melb2$Distance, melb2$PricePerSQM)
```
Dari plot di atas ditemukan bahwa banyak housing yang terjual berdekatan dengan CBD. Namun, setelah melakukan pengecekan dengan cor(), terdapat korelasi negatif antara jarak CBD dengan harga per meter persegi. Sehingga, tidak ada hubungan antara jarak CBD dengan harga.
```{r}
#Plotting Price PerSQM and number of rooms
boxplot(melb2$PricePerSQM~ melb2$Rooms)
```
Dari plot di atas, ditemukan bahwa housing yang memiliki ruangan dua memiliki median harga per meter persegi tertinggi.

```{r}
#Plotting Price PerSQM and number of bedroom
boxplot(melb2$PricePerSQM~ melb2$Bedroom2)
```
Dari plot di atas, ditemukan bahwa housing yang memiliki dua ruangan tidur memiliki median harga per meter persegi tertinggi.

```{r}
#Plotting Price PerSQM and number of bathroom
boxplot(melb2$PricePerSQM~ melb2$Bathroom)
```
Dari plot di atas, ditemukan bahwa housing yang memiliki dua ruangan tidur memiliki median harga per meter persegi tertinggi.


```{r}
#Plotting Price PerSQM and region
par(cex = 0.4) #Reducing Text size
plot(melb2$PricePerSQM~ melb2$Regionname)
```
Dari boxplot di atas, ditemukan bahwa Southern Metropolitan memiliki median harga per meter persegi tertinggi, sedangkan South-Eastern Metropolitan memiliki harga terendah.

***4. SUMMARY***

Dalam data properti yang disajikan, properti yang paling banyak terjual berada di suburb Reservoir.

Namun, properti yang paling mahal adalah sebuah townhouse yang terletak di area suburb East Melbourne. Properti ini memiliki luas sekitar 15703.536 meter persegi per meter persegi (pSQM), menjadikannya salah satu yang paling mahal dalam dataset ini. Townhouse ini memiliki 2 ruangan, 2 kamar tidur, dan 4 kamar mandi. Terletak di wilayah Southern Metropolitan, properti ini menawarkan kemewahan dan fasilitas yang sangat eksklusif, mencerminkan gaya hidup yang mewah dan nyaman bagi pemiliknya.


----------------------------------------
DOT POINTS

1. Dalam data yang disajikan, properti yang paling banyak terjual berada pada suburb Reservoir

2. Housing Termahal:
- Area suburb East Melbourne (harga =  15703.536 pSQM)
- Tipe Housing Townhouse
- Memiliki 2 Ruangan
- Memiliki 2 Bedroom
- Memiliki 4 Bathroom
- Lokasi di Southern Metropolitan


